Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-11 Papers/ms.tex
Working on the table

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
$W_{\rm src}$ &		Typical width of source blobs	& \\
$W_{\rm lens}$&		Typical width of lens blobs	& \\
{\bf Lens Blob Parameters}\\
$(x_i^{\rm src}, y_i^{\rm src})$
$M_i$  &
$v_i$  &
{\bf Source Blob Parameters}\\
{\bf Smooth Lens Parameters}\\
{\bf Noise Parameters}\\
{\bf Data}\\
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}

>>>>

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
\hline
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
$W_{\rm src}$ &		Typical width of source blobs	& \\
$W_{\rm lens}$&		Typical width of lens blobs	& \\
\hline
{\bf Source Blob Parameters}\\
\hline
$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
$w_i$  & Blob width & Exponential(mean=$W_{\rm src}$)\\
\hline
{\bf Lens Blob Parameters}\\
\hline
$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & \\
$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
$v_i$  & Blob width & Exponential(mean=$W_{\rm lens}$)\\
\hline
{\bf Smooth Lens Parameters}\\
\hline
$b$\\
$q$\\
$(x_c^{\rm SIE}, y_c^{\rm SIE})$\\
$\theta$\\
$\gamma$\\
$\theta_\gamma$\\
\hline
{\bf Noise Parameters}\\
\hline
$\sigma_0$\\
$\sigma_1$\\
\hline
{\bf Data}\\
\hline
$D_{ij}$
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}
